A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-19 analysis/paper/paper.Rmd
commit before pulling

```{r, figure-KWL-map, fig.cap = "The location of Kiwulan and other places with the European forts in northern Taiwan mentioned in the text (map modified from Wang and Marwick, 2020). Map data from naturalearthdata.com."}

>>>>

```{r site-map, figure-KWL-map, fig.cap = "The location of Kiwulan and other places with the European forts in northern Taiwan mentioned in the text (map modified from Wang and Marwick, 2020). Map data from naturalearthdata.com."}
